\documentclass{article}


% \usepackage{arxiv}
\usepackage[final]{neurips}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsmath, amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{color}
\usepackage{verbatimbox}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{bbding}
\usepackage{pifont}
\usepackage{wasysym}
\usepackage{bbding}
\usepackage{pifont}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{amsmath}
\usepackage{adjustbox}
\usepackage{cleveref}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}
\usepackage[numbers]{natbib}

\usepackage{wrapfig}
\definecolor{light-gray}{gray}{0.95}
\usepackage{tcolorbox}

\usepackage{mathtools}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%

\usepackage{subcaption}% <-- added
% \usepackage[showframe]{geometry}
\usepackage[justification=justified,skip=5pt]{caption}
\captionsetup*[table]{aboveskip=5pt, belowskip=5pt}

%New colors defined below
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.96}

\setlist[itemize]{leftmargin=*}
\setlist[enumerate]{leftmargin=*}
\graphicspath{ {./images/} }

%Code listing style named ''mystyle''
\lstdefinestyle{mystyle}{
  backgroundcolor=\textcolor{backcolour}, commentstyle=\textcolor{codegreen},
  keywordstyle=\textcolor{magenta},
  numberstyle=\tiny\textcolor{codegray},
  stringstyle=\textcolor{codepurple},
  basicstyle=\ttfamily\footnotesize,
  breakatwhitespace=false,         
  breaklines=true,                 
  captionpos=b,                    
  keepspaces=true,                 
  numbers=left,                    
  numbersep=5pt,                  
  showspaces=false,                
  showstringspaces=false,
  showtabs=false,                  
  tabsize=2
}

%''mystyle'' code listing set
\lstset{style=mystyle}

\usepackage[strict]{changepage}
\usepackage{xcolor}
\usepackage{framed}
\definecolor{demonstrationshade}{rgb}{0.95,0.95,1}
\definecolor{promptshade}{rgb}{0.95,0.95,1}
\newenvironment{demonstration}{%
  \def\FrameCommand{%
    \hspace{1pt}%
    {\textcolor{black}\vrule width 2pt}%
    {\textcolor{demonstrationshade}\vrule width 4pt}%
    \colorbox{demonstrationshade}%
  }%
  \MakeFramed{\advance\hsize-\width\FrameRestore}%
  \noindent\hspace{-4.55pt}% disable indenting first paragraph
  \begin{adjustwidth}{1pt}{7pt}%
  \vspace{2pt}\vspace{2pt}%
}
{%
  \vspace{2pt}\end{adjustwidth}\endMakeFramed%
}

\newcommand{\yongfeng}[1]{{\small\textcolor{blue}{\bf Yongfeng: #1}}}
\newcommand{\lingyao}[1]{{\small\textcolor{green}{\bf Lingyao: #1}}}
\newcommand{\wenyue}[1]{{\small\textcolor{red}{\bf Wenyue: #1}}}
\newcommand{\oliver}[1]{{\small\textcolor{magenta}{\bf Oliver: #1}}}

\makeatletter
\def\thanks#1{\protected@xdef\@thanks{\@thanks
        \protect\footnotetext{#1}}}
\makeatother

% \title{Game Theory with Negotiation:\\ How to obtain Pareto optimal Nash Equilibrium for LLM-based Agents}

% \title{AI4History: An Example of Large Language Model-based Multi-Agent Simulation of World Wars}

% \title{Game-theoretic LLM:\\ Agent Workflow for Negotiation Games}

\title{Towards a Tokenomics-Driven Decentralized Ecosystem for LLM Agents}

\author{
% \vspace{.5mm}
Xi Zhu$^1$\quad
Zhuoqiao Shen$^2$\quad 
Shuhang Lin$^1$\quad 
Minghao Guo$^1$\quad
Yongfeng Zhang$^{1}$\thanks{Corresponding Email: xi.zhu@rutgers.edu, yongfeng.zhang@rutgers.edu. }\\
  $^1$Rutgers University\;\;\;  $^2$Independent Researcher\;\;\;
}

% \vspace{0.4cm}

\begin{document}

\maketitle

\noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}}
\tableofcontents
\noindent\makebox[\linewidth]{\rule{\textwidth}{1pt}}
\vspace{0.2cm}
\noindent

\begin{abstract}

Modern online platforms are predominantly centralized, where data storage, algorithmic governance, and reward distribution remain under the dominance of platform operators. This motivates a foundational rethinking of application architecture and organization. In this paper, we posit that next-generation internet applications are evolving towards decentralized ecosystems that enable self-governance without centralized enforcement. To ground this vision, we instantiate DeQA, a decentralized knowledge question answering ecosystem that aligns user incentives through a self-enforcing tokenomics-knowledge dual loop, supported by a blockchain-based infrastructure for transparent and tamper-resistant coordination.

In DeQA, users dynamically assume the roles of consumers, producers, and validators: consumers issue token-backed queries, producers provide knowledge-intensive services, and validators ensure reliable matching through consensus. Along this line, we introduce a decentralized validation paradigm called Proof-of-Intelligence (PoI), where heterogeneous validators leverage their knowledge to assess query–responder alignment.
Validators stake tokens and are rewarded when their judgments align with the majority, forming a self-enforcing incentive structure that promotes truthful effort and deters free-riding.

To prevent moral hazard and low-quality validation, we model the strategic interactions among producers, consumers, and validators within a unified game-theoretic framework. Specifically, we first establish validator incentive compatibility (IC) to guarantee truthful aggregation of dispersed knowledge, then we derive threshold-optimal policies for consumer subscription and producer promotion under individual rationality (IR). Combining these conditions, we prove the existence of a symmetric Bayesian-Nash equilibrium (BNE) that ensures consistent strategic behavior, rational cooperation, and stable query-responder matching. Extensive simulations validate that DeQA enables a self-enforcing ecosystem with truthful contributions and maximum social welfare.

\end{abstract}

\textit{Note: Sections 4, 5, and 6 are independent of one another and can be read in any order. Each section is self-contained and does not require prior knowledge of the others to be fully understood.}


\input{sections/Introduction}

\input{sections/Methodology}

\input{sections/Experiments}

\input{sections/Related Works}

\input{sections/Conclusion}

% \input{sections/Introduction_2}

% \input{sections/Related Work}

% \input{sections/Preliminary for Game Theory}

% \input{sections/Complete-information Games}

% \input{sections/Incomplete-information Game with Negotiation}

% \input{sections/Detailed Observation on LLM's Rationality}

% \input{sections/Conclusion_2}

% \input{sections/Future Directions}

\bibliographystyle{unsrt}  
\bibliography{references} 
\end{document}


