\section{Conclusion}
\label{sec:conclusion}

As LLM agents evolve into an interconnected society of autonomous, cross-organizational actors, the question of how to coordinate their collaboration without centralized authority becomes both urgent and foundational.
This paper addresses this challenge by proposing a tokenomics-driven decentralized ecosystem in which the trust crisis---arising from capability limitations, strategic misbehavior, near-zero deployment costs, and the structural deficiencies of centralized orchestration---is resolved through self-enforcing economic protocols rather than central control.
The ecosystem is organized around three dynamically interchangeable roles (consumers, producers, and validators), coordinated through a novel Proof-of-Intelligence (PoI) validation mechanism and a tokenomics--knowledge dual loop that aligns individual rationality with collective welfare.
A key design principle is \textit{architectural heterogeneity}: by mandating that validators employ model architectures distinct from the producer under evaluation, the mechanism substantially reduces correlated errors and approximates the independence assumption that underpins reliable consensus formation.
Within a unified game-theoretic framework, we formalize the Bayesian validation game, establish validator incentive compatibility (Theorem~\ref{Strict IC for Validators}), derive threshold-optimal policies for producers (Theorem~\ref{IR for Producers}) and consumers (Theorem~\ref{IR-based Policy for Consumers}), and prove the existence of a symmetric Bayesian--Nash equilibrium (Theorem~\ref{Symmetric Bayesian Nash Equilibrium}) that guarantees rational cooperation without centralized enforcement.
As a case study, we instantiate the framework as a decentralized question answering system (DeQA) and demonstrate through extensive simulation that the mechanism drives agent communities toward truthful contribution and improved social welfare.

\textbf{Limitations.}
We acknowledge several simplifying assumptions that constrain the scope of our current results.

\textit{(i) Bounded collusion.}
Our robustness analysis (\S\ref{sec:robustness}) shows that IC is preserved under bounded Sybil attacks ($k < \lfloor n/2 \rfloor$ adversarial validators) and bounded correlation ($\rho < \rho^*$). However, an adversary controlling a \textit{majority} of validators in a single committee could still subvert the consensus. Extending the framework with randomized committee assignment from a qualified pool, collusion-resistant mechanism design~\cite{miller2005eliciting}, or cryptographic commit-reveal schemes would harden the mechanism beyond the $k < \lfloor n/2 \rfloor$ bound.

\textit{(ii) Static quality assumption.}
We treat agent quality $q_u$ as a static, exogenous parameter drawn from a fixed distribution. In reality, agents can improve their knowledge bases over time (e.g., through fine-tuning or retrieval augmentation), and a richer model would capture this dynamic quality evolution endogenously, potentially leading to more complex equilibrium dynamics.

\textit{(iii) Residual correlation beyond the analyzed regime.}
Our robustness analysis shows that the mechanism tolerates substantial residual correlation under a latent-factor mixture model ($\rho < \rho^*$, \S\ref{sec:robustness}(B)), but real-world correlation structures may be non-uniform (e.g., models from the same family may be more correlated than models from different families). Extending the analysis to block-correlated or hierarchically correlated validators remains an open problem.

\textit{(iv) Synthetic simulation.}
Our DeQA case study uses synthetic agents with parameterized quality distributions rather than production-grade LLMs. Deploying the ecosystem with real language models---where quality is task-dependent, non-stationary, and harder to characterize by a single scalar---remains a crucial next step toward practical validation.

\textit{(v) Token macroeconomics.}
The current model operates with a fixed token supply and does not analyze long-run macroeconomic dynamics such as token inflation, deflation through agent exit, or wealth concentration effects. A thorough analysis of the token supply dynamics under repeated play would complement the static equilibrium results.

We discuss promising extensions, a detailed research roadmap, and the long-term vision for the ecosystem as a coordination layer for the agent society in \Cref{sec:future_work}.
